Analysis and approximation of mixed-dimensional PDEs on 3D-1D domains coupled with Lagrange multipliers

### 2020-04-07 arxiv/intersection.tex
arxived

%\documentclass[tikz,border=3mm]{standalone}
%\usetikzlibrary{calc}
%\usetikzlibrary{shapes, snakes, patterns, arrows}
%\begin{document}

\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
\pgfmathsetmacro{\factor}{1/sqrt(2)};

\coordinate  (A) at (-2.5,1.5,-2.1*\factor);
\coordinate  (B) at (3.8,4,0*\factor);
\coordinate  (C) at (3.6,-2,2*\factor);
\coordinate  (D) at (6.5,2.7,8*\factor);
\draw[thick, black,    fill=white!90!gray, opacity=1] (A) --(B)--(C)--cycle;
\draw[ thick,black,  fill=gray!60!, opacity=0.7] (D) --(B)--(C)--cycle;
\draw[thick,gray!60!] (D) --(A);
\node [font=\Large, right] at (3.5, -2.5) {$\omega_j $};

@@

\draw[dashed, very thick, purple, opacity=.4] (1, 3.05) ellipse (1.5 and 0.3);
\draw[dashed, very thick, purple, opacity=.4] (1, -0.65) ellipse (1.5 and 0.3);

\fill [purple, opacity=0.3]  (-0.5, -0.65) arc (180:360:1.5 and 0.3) -- (2.5, 3.05) arc (0:180:1.5 and -0.3);
\node [font=\Large, right, purple] at (-2, 0) {$\Gamma_{\omega_j \cap \Lambda}$};

>>>>

%\documentclass[tikz,border=3mm]{standalone}
%\usetikzlibrary{calc}
%\usetikzlibrary{shapes, snakes, patterns, arrows}
%\begin{document}
\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]

\pgfmathsetmacro{\factor}{1/sqrt(2)};

%tetrahedron
\coordinate  (A) at (-2.5,1.5,-2.1*\factor);
\coordinate  (B) at (3.8,4,0*\factor);
\coordinate  (C) at (3.6,-2,2*\factor);
\coordinate  (D) at (6.5,2.7,8*\factor);
\draw[thick, black,    fill=white!90!gray, opacity=1] (A) --(B)--(C)--cycle;
\draw[ thick,black,  fill=gray!60!, opacity=0.7] (D) --(B)--(C)--cycle;
\draw[thick,gray!60!] (D) --(A);
\node [font=\Large, right] at (3.5, -2.5) {$\omega_j $};

@@

%intersection
\draw[dashed, very thick, purple, opacity=.4] (1, 3.05) ellipse (1.5 and 0.3);
\draw[dashed, very thick, purple, opacity=.4] (1, -0.65) ellipse (1.5 and 0.3);
\draw[dashed, very thick, purple, opacity=.4] (1, 1.5) ellipse (1.5 and 0.3);
\fill [purple, opacity=0.3]  (2.5, -0.65) arc (360:280:1.5 and 0.3) -- (-0.5, 0.75) -- (-0.5, 2.55) -- (0.3, 2.8) arc (118:0:1.5 and -0.3);
\node [font=\Large, right, purple] at (-2, -0.1) {$\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$};
